Assembly Quality Metrics - Quast Results

### 2019-02-07 notebooks/assembly_metrics.Rmd
added boxplots on summary metrics to verify similarity between isolates from animal species and sequencer

```{r, include = FALSE}
pacman::p_load(dplyr, ggplot2, tidyr, cowplot, viridis, forcats, radiant.data, purrr, phangorn, gridExtra, ggtree, htmlTable, ape, cluster, tibble, magrittr)

@@

create_df <- function(df) {
  df <- df %>%
    rename(ctg_0_bp = X..contigs.....0.bp.,
           ctg_1000_bp = X..contigs.....1000.bp.,
           ctg_5000_bp = X..contigs.....5000.bp.,
           ctg_10000_bp = X..contigs.....10000.bp.,
           ctg_25000_bp = X..contigs.....25000.bp.,
           ctg_50000_bp = X..contigs.....50000.bp.,
           tot_len_0_bp = Total.length.....0.bp.,
           tot_len_1000_bp = Total.length.....1000.bp.,
           tot_len_5000_bp = Total.length.....5000.bp.,
           tot_len_10000_bp = Total.length.....10000.bp.,
           tot_len_25000_bp = Total.length.....25000.bp.,
           tot_len_50000_bp = Total.length.....50000.bp.,
           no_of_contigs = X..contigs,
           no_of_misassemblies = X..misassemblies,
           no_of_misassembled_ctg = X..misassembled.contigs,
           no_of_local_misassemblies = X..local.misassemblies,
           unaligned_contigs = X..unaligned.contigs,
           N_per_100kbp = X..N.s.per.100.kbp,
           mismatches_per_100kbp = X..mismatches.per.100.kbp,
           indels_per_100kbp = X..indels.per.100.kbp,
           genes = X..genes,
           GC = GC....,
           duplication_ratio = Duplication.ratio,
           largest_contig = Largest.contig)
  return(df)
}

@@

>>>>

```{r, include = FALSE}
pacman::p_load(dplyr, ggplot2, tidyr, cowplot, scales)

@@

create_df <- function(df) {
  df <- df %>%
    dplyr::rename(ctg_0_bp = X..contigs.....0.bp.,
           ctg_1000_bp = X..contigs.....1000.bp.,
           ctg_5000_bp = X..contigs.....5000.bp.,
           ctg_10000_bp = X..contigs.....10000.bp.,
           ctg_25000_bp = X..contigs.....25000.bp.,
           ctg_50000_bp = X..contigs.....50000.bp.,
           tot_len_0_bp = Total.length.....0.bp.,
           tot_len_1000_bp = Total.length.....1000.bp.,
           tot_len_5000_bp = Total.length.....5000.bp.,
           tot_len_10000_bp = Total.length.....10000.bp.,
           tot_len_25000_bp = Total.length.....25000.bp.,
           tot_len_50000_bp = Total.length.....50000.bp.,
           no_of_contigs = X..contigs,
           no_of_misassemblies = X..misassemblies,
           no_of_misassembled_ctg = X..misassembled.contigs,
           no_of_local_misassemblies = X..local.misassemblies,
           unaligned_contigs = X..unaligned.contigs,
           N_per_100kbp = X..N.s.per.100.kbp,
           mismatches_per_100kbp = X..mismatches.per.100.kbp,
           indels_per_100kbp = X..indels.per.100.kbp,
           genes = X..genes,
           GC = GC....,
           duplication_ratio = Duplication.ratio,
           largest_contig = Largest.contig)
  return(df)
}

@@

# Summarised assembly stats
## Summary stats per animal species
```{r}
p1 <- ggplot(metrics2, aes(species, N50)) +
  stat_boxplot(geom = "errorbar", width = 0.4) +
  geom_boxplot() +
  scale_y_continuous(labels = comma) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 8))

p2 <- ggplot(metrics2, aes(species, no_of_contigs)) +
  stat_boxplot(geom = "errorbar", width = 0.4) +
  geom_boxplot() +
  labs(y = "No. of contigs") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 8))

p3 <- ggplot(metrics2, aes(species, largest_contig)) +
  stat_boxplot(geom = "errorbar", width = 0.4) +
  geom_boxplot() +
  labs(y = "Largest contig") +
  scale_y_continuous(labels = comma) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 8))

p4 <- ggplot(metrics2, aes(species, as.numeric(no_of_misassemblies))) +
  stat_boxplot(geom = "errorbar", width = 0.4) +
  geom_boxplot() +
  labs(y = "No. of misassemblies") +
  scale_y_continuous(labels = comma) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 8))

plot_grid(p1, p2, p3, p4, ncol = 2, nrow = 2, align = "v")
```

## Summary stats per sequencing method
```{r}
p5 <- ggplot(metrics2, aes(sequencer, N50)) +
  stat_boxplot(geom = "errorbar", width = 0.4) +
  geom_boxplot() +
  scale_y_continuous(labels = comma) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 8))

p6 <- ggplot(metrics2, aes(sequencer, no_of_contigs)) +
  stat_boxplot(geom = "errorbar", width = 0.4) +
  geom_boxplot() +
  labs(y = "No. of contigs") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 8))

p7 <- ggplot(metrics2, aes(sequencer, largest_contig)) +
  stat_boxplot(geom = "errorbar", width = 0.4) +
  geom_boxplot() +
  labs(y = "Largest contig") +
  scale_y_continuous(labels = comma) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 8))

p8 <- ggplot(metrics2, aes(sequencer, as.numeric(no_of_misassemblies))) +
  stat_boxplot(geom = "errorbar", width = 0.4) +
  geom_boxplot() +
  labs(y = "No. of misassemblies") +
  scale_y_continuous(labels = comma) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 8))

plot_grid(p5, p6, p7, p8, ncol = 2, nrow = 2, align = "v")
```
